---
title: "Homework 3"
author: "Karina Álvarez"
date:  "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output: html_document
---

####Install necessary packages 
```{r setup, include=FALSE}

library(dplyr)
library(gapminder)

data(gapminder)
head(gapminder)
```


#### Q1.What class is the gapminder dataset? 

```{r}
class(gapminder)
```



#### Q2.Filter a section of gapminder with a life expectancy smaller than 29.

```{r}
gapminder %>% 
  filter(lifeExp <29)
```




#### Q3. Filter the dataset for the country Rwanda and for years greater than 1979. 

```{r}
gapminder %>%
  filter(country == "Rwanda", year >1979)
  
```




#### Q4. Create a new dataset from gapminder excluding the column gdpPercap. 

```{r}
gapminder_data <- gapminder %>%
  select(-gdpPercap)
gapminder_data
  
```




#### Q5. Arrange the dataset in ascending order of lifeExp

```{r}
gapminder %>%
  arrange(lifeExp)
```




#### Q6. Arrange the dataset in descending order of lifeExp.

```{r}
gapminder%>%
  arrange(desc(lifeExp))
```




#### Q7. Create a new dataset with only the columns year and lifeExp. 

```{r}
gapminder_data_new <- gapminder%>%
  select(year:lifeExp)
gapminder_data_new
```




#### Q8. Filter the dataset for the country Cambodia and show only the columns year and lifeExp.

```{r}
gapminder %>%
  filter(country == "Cambodia") %>%
  select(year:lifeExp)

```




#### Q9. Select only the countries in Africa.

```{r}
gapminder%>%
  filter(continent=="Africa")
```




#### Q10. Create a new column called lifeExp_months that shows life expectancy in months.

```{r}
newgapminder <- gapminder %>%
  mutate(lifeExp_months= lifeExp * 12)

newgapminder %>%
  select(lifeExp, lifeExp_months, everything())
```

