---
title: "Homework 1"
author: "Karina Álvarez"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output: html_document
---
<br>
<br>
<br>

#### Q1. Create an object called height with the value 175. Print it. (Crea un objeto llamado height con el valor 175. Muéstralo en pantalla.)

```{r}
height <- 175 
height
```


#### Q2. Calculate the result of 25 * 4 - 10. (Calcula el resultado de 25 * 4 - 10.)

```{r}
25 * 4 -10
```


#### Q3. Use the function sqrt() to calculate the square root of 81. (Usa la función sqrt() para calcular la raíz cuadrada de 81.)

```{r}
sqrt(81)
```

#### Q4. Assign the phrase “R is fun!” to an object called message. Print it. (Asigna la frase “R is fun!” a un objeto llamado message. Muéstralo.)

```{r}
Message= "R is fun!"
Message 
```

#### Q5. Create two objects a <- 10 and b <- 5. Calculate their sum and store it in c. (Crea dos objetos a <- 10 y b <- 5. Calcula su suma y guárdala en c.)

```{r}
a <- 10
b <-5
a + b 
c <- a +b 
c
```

#### Q6. Test whether 15 is greater than 20. (Verifica si 15 es mayor que 20.)

```{r}
15>20
```

#### Q7. Check the class of the object "Hello World". (Verifica la clase del objeto "Hello World".)

```{r}
obj1 <- "Hello World"
class(obj1)
```


#### Q8. Run the following code chunk:
- Observe the warnings that appear. (Observa las advertencias que aparecen.)
- Modify the chunk options to suppress warnings without changing the code itself. (Modifica las opciones del chunk para apagar la advertencia sin cambiar el código.)

```{r, warning=FALSE}
log(-1)
```

#### Q9. Run the following code chunk: - Observe the messages that appear. (Observa los mensajes que aparecen.)

Modify the chunk options to suppress messages without changing the code itself. (Modifica las opciones del chunk para apagar mensajes sin cambiar el código.)

```{r, warning=FALSE}
library(dplyr)
```

#### Q10. Use R’s help system to find out what the function mean() does. (Usa el sistema de ayuda de R para averiguar qué hace la función mean().)

```{r}
?mean()
```


### DONE. 

